---
title: "LMM considerations"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# One factor rm ANOVA, categorical fixed effect 
```{r message=FALSE, warning=FALSE, include=FALSE}
library(lme4)
library(afex)

df1 <- read.csv2("one_factor_rm_cat.csv", header=T,dec=",")
df1$situation <- factor(df1$situation)
```

Model works fine with random intercept only:
```{r}
# lmer model, random intercept
model1 <- lmer(measure ~ situation + (1|id),df1)
summary(model1)
```


Adding a random slope makes it unidentifiable 
```{r error = TRUE}
# lmer model, random intercept + random slope
model2 <- lmer(measure ~ situation + (1+situation|id),df1)
```

# Continuous predictor (fixed effect) works
Adding a random slope works when the predictor is continuous
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
### fixed effect, random intercept & slope
df2 <- read.csv2("one_factor_rm_cont.csv", header=T,dec=",")
# rescale predictor (otherwise conversion warning)
mu_x <- mean(df2$acceleration)
sig_x <- sd(df2$acceleration)
df2$acceleration_s <- (df2$acceleration-mu_x)/sig_x # standardize predictor
```

```{r}
model3 <- lmer(delta_distance ~ acceleration_s + (1+acceleration_s|id),df2) #standardized predictor needed for convergence
summary(model3)
```


# two factor mixed anova

```{r message=FALSE, warning=FALSE, include=FALSE}
df3 <- read.csv2("two_factor_rm.csv", header=T,dec=",")
df3$stage<-factor(df3$stage)
df3$group<-factor(df3$group)
```

# model, random intercept 
Random intercept only works:
```{r}
model4 <- lmer(dv ~ group*stage+(1|id),df3)
summary(model4)
```

# model, random intercept + random slope per factor
This model is already unidentifiable
```{r, error = TRUE}
model5 <- lmer(dv ~ group*stage+(1+group|id)+(1+stage|id),df3)
```

#maximum model? random slope for interaction
Also unidentifiable
```{r,error = TRUE}
model6 <- lmer(dv ~ group*stage+(group*stage|id),df3)
```
